\section{Formal description of the
	experiment}\label{formal-description-of-the-experiment}

In the experiment we seek to:

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	Check the functionality of the experimental software system.
	
	\begin{itemize}
		\tightlist
		\item
		Check if the framework matches initial functional properties.
		\item
		Test for stability, performance, and usability in real case scenarios.
	\end{itemize}
	
	\item
	Evaluation of \glspl{unmanned_aerial_vehicle} (having \gls{wifi} \glspl{access_point}) layout optimization algorithms.
	
	\begin{itemize}
		\tightlist
		\item
		Evaluation for the correctness of suggested positions for \glspl{uav}. We suppose that the framework is intended to optimize positions for \acrshort{uavbs}, but in the experiment we use \glspl{ap} placed on the ground instead.
		\item
		Measurement of accuracy, stability, and performance of the optimization algorithms.
	\end{itemize}
	
\end{enumerate}


\subsection{Main information}\label{main-information}

The main purpose of the experiment is to optimize the location of \glspl{access_point} in such a way that network throughput and \acrshort{rss} of \glspl{ue} is maximized.

For that, we design our experiment in the following way:

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	\gls{ap} located in the space without any obstacles. They are surrounded by
	\glspl{ue}.
	\item
	\glspl{ue} connect to \glspl{ap}. \acrshort{rss} and throughput are evaluated via specially designed framework (combination of \gls{gps_tracker}, \gls{gps_android}, \gls{gps_frontend}).
	\item
	\Glspl{ue} sends messages to the central server.
	\item
	An operator has access to a control interface, where he can analyze received data and run optimization algorithms to find out the best positions for \glspl{ap}.
	\item
	Once a better-suggested position for \gls{ap} is found, the \gls{ap} will be moved there.
	\item
	The experiment goes to the third step and repeats until no significant improvement regarding \acrshort{rss} and speed rate will be observed.
\end{enumerate}

The experiment repeated three times with different initial positions. Test sets:

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	Near-Optimal (\glspl{ap} are equidistant from \glspl{ue}  according to K-Means), described in Section \ref{near-optimal-layout}.
	\item
	Uniform (\glspl{ap} has the same distance to \gls{command_n_center}), described in Section \ref{uniform-layout}.  
	\item
	Sub-Optimal (\glspl{ap} are surrounded by \glspl{ue}), described in Section \ref{sub-optimal-layout}.
	
	
\end{enumerate}

For each test case, we expect that:

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	Minimization of the distance between \glspl{ue} and \glspl{ap} will lead to \glspl{rss} gain and throughput increase.
	\item
	The interference effect may be visible - in the sub-optimal
	placements, it should decrease the throughput;
\end{enumerate}