\section{Experiment requirement}\label{experiment-requirement}

\subsection{Hardware Equipment}\label{hardware-equipment}

\begin{itemize}
\tightlist
\item
  6 cellphones with \gls{android} \acrshort{os} (version 5.0 and above). Phones have a dedicated \gls{gnss} module and an \gls{wifi} adapter.
\item
  3 external \gls{wifi} adapters with managed-mode capability.

  \begin{itemize}
  \tightlist
  \item
    Model: AWUS036NEH
  \item
    Height of antenna  for \gls{command_n_center}: 17.2 cm
  \item
    Height of antenna  for \acrshort{ap}: 11 cm
  \end{itemize}
\item
  3 Laptops
\item
  One ruler
\end{itemize}

\subsection{Software Equipment}\label{software-equipment}

\subsubsection{For \glsentrytext{ue} }

\begin{itemize}
\tightlist
\item
  \gls{android}-enabled smartphone (version 5.0 and above).

  \begin{itemize}
  \tightlist
  \item
  	\Gls{gps_android} installed.
    \end{itemize}
\end{itemize}

\subsubsection{For \glsentrytext{command_n_center} }\label{for-command-center-cnc}

\begin{itemize}
\tightlist
\item
  The host machine

\begin{itemize}
	\tightlist
	\item
	Any Debian-based \acrshort{os} (Debian, Ubuntu, etc.).
	\item
	\gls{virtualbox} + \gls{virtualbox_ext_pack} latest version installed.
	\item
	\gls{python3} + \gls{ansible} (for convenient configuration) installed.
	\item
	\texttt{openssh-server} package installed.
\end{itemize}
\item
  The virtual \gls{command_n_center} machine

  \begin{itemize}
  \tightlist
  \item
    \texttt{dnsmasq}, \texttt{hostapd} packages installed.
  \item
    \texttt{openssh-server} package installed.
  \item
    \texttt{docker} and \texttt{docker-compose} packages installed.
  \item
  	\texttt{iperf3} package installed.

    \begin{itemize}
    \tightlist
    \item
      \gls{mongodb} container.
    \item
      \gls{rabbitmq} container.
    \item
      \gls{mqtt} broker container.
    \item
      \gls{python3} container.
    \item
      \gls{nginx} container.
    \item
      \gls{nodejs} container.
    \end{itemize}
  \end{itemize}
\end{itemize}

\subsubsection{For \glsentrytext{access_point}}\label{for-aps}

\begin{itemize}
\tightlist
\item
The host machine

\begin{itemize}
	\tightlist
	\item
	Any Debian-based \acrshort{os} (Debian, Ubuntu, etc.).
	\item
	\gls{virtualbox} + \gls{virtualbox_ext_pack} latest version.
	\item
	\gls{python3} + \gls{ansible} (for convenient configuration) installed.
	\item
	\texttt{openssh-server}.
\end{itemize}
\item
  The virtual \acrshort{ap} machine

  \begin{itemize}
  \tightlist
  \item
    Any Debian-based \acrshort{os} (Debian, Ubuntu, etc.).
  \item
    \texttt{dnsmasq}, \texttt{hostapd} installed.
  \item
    \texttt{iperf3} installed.
  \item
    \texttt{openssh-server} installed.
  \item
    \texttt{docker} and \texttt{docker-compose} installed.

    \begin{itemize}
    \tightlist
    \item
      \acrshort{ftp}-server container.
    \end{itemize}
  \end{itemize}
\end{itemize}
