
\newglossaryentry{gps_frontend}{name={GPS\_Frontend},description={A web-based application to provide user interface to interact with \gls{gps_tracker}.}}

\newglossaryentry{gps_tracker}{name={GPS\_Tracker},description={A name of the framework and as well a name for the backend software running for processing and storing telemetry data}}

\newglossaryentry{gps_android}{name={GPS\_Android},description={An Android application to send the telemetry information about the current mobile network from the users' phones to \gls{gps_tracker}.}}

\newglossaryentry{telemetry}{name={Telemetry},description={Messages from the phones insalled \gls{gps_android}. Includes \acrshort{rss} level, uplink/downlink throughput measurement, \acrshort{gnss} coordinates.}}

\newglossaryentry{broker}{name={Broker},description={A broker component coordinates communication of requests from client to server and also coordinates returning the results from server to client \cite{2}}}

\newglossaryentry{mqtt_protocol}{name={Message Queuing Telemetry Transport},description={An publisher/subscriber-based application protocol running over TCP/IP, suitable for IoT application.}}

\newglossaryentry{json_format}{name={JavaScript Object Notation},description={a lightweight data-interchange format.}}

\newglossaryentry{mongodb}{name={MongoDB},description={A NoSQL database storing data in BSON (Binary \acrshort{json}) format \cite{mongodb}}}

\newglossaryentry{celery}{name={Celery},description={A framework to implement a program using "Worker" architecture design  \cite{celery}}}

\newglossaryentry{rabbitmq}{name={RabbitMQ},description={An in-memory queuing message broker \cite{rabbitmq}}}

\newglossaryentry{user_equipment}{name={User Equipment},description={A mobile terminal which transmits data via the radio link.}}

\newglossaryentry{access_point}{name={Access Point},description={A laptop with an external \gls{wifi} adapter.}}

\newglossaryentry{command_n_center}{name={Command Center},description={A central server where the system core is running. All measurement analysis and UI interactions perform here.}}

\newglossaryentry{unmanned_aerial_vehicle}{name={Unmanned Aerial Vehicle},description={A vehicle having \gls{access_point} on the board.}}

\newglossaryentry{received_signal_strength}{name={Received Signal Strength},description={The estimated value of signal power for the radio signal. The greater the RSS value, the stronger the signal.}}

\newglossaryentry{wifi}{name={Wi-Fi},description={Wi-Fi a family of wireless networking technologies, based on the IEEE 802.11 family of standards, which are commonly used for local area networking of devices and Internet access. \cite{1}}}

\newglossaryentry{python}{name={Python},description={Python is an interpreted, high-level, general-purpose programming language.}}

\newglossaryentry{nginx}{name={nginx},description={is an HTTP and reverse proxy server, a mail proxy server, and a generic TCP/UDP proxy server \cite{nginx}}}

\newglossaryentry{nodejs}{name={NodeJS},description={Node.js is a JavaScript runtime built on Chrome's V8 JavaScript engine \cite{nodejs}Facc }}

\newglossaryentry{ansible}{name={Ansible},description={Ansible is a simple, but powerful, server and configuration management tool \cite{ansible}}}

\newglossaryentry{android}{name={Android},description={A modern operation system for mobile phones developed by Google}}




\newacronym{ftp}{FTP}{File Transport Protocol}

\newacronym{os}{OS}{Operating System}

\newacronym{ap}{AP}{Access Point}

\newacronym{snat}{SNAT}{Source \acrfull{nat}}
\newacronym{dnat}{DNAT}{Destination \acrfull{nat}}
\newacronym{nat}{NAT}{Network Address Translation}

\newacronym{http}{HTTP}{Hyper Text Transfer Protocol}

\newacronym{mvvm}{MVVM}{Model-View-ViewModel}

\newacronym{dhcp}{DCHP}{Dynamic Host Configuration Protocol}
\newacronym{dns}{DNS}{Domain Name System}
\newacronym{ip}{IP}{Internet Protocol}
\newacronym{icmp}{ICMP}{Internet Control Message Protocol}

\newacronym{cnc}{CnC}{Command Center}
\newacronym{mqtt}{MQTT}{Message Queuing Telemetry Transport}

\newacronym{ue}{UE}{\gls{user_equipment}}
\newacronym{uav}{UAV}{\gls{unmanned_aerial_vehicle}}

\newacronym{rss}{RSS}{Received Signal Strength}

\newacronym{json}{JSON}{\gls{json_format}}


\newacronym{gnss}{GNSS}{Global Navigation Satellite System}

\newacronym{gps}{GPS}{Global Positioning System}
