
\newglossaryentry{gps_frontend}{name={GPS\_Frontend},description={A web-based application to provide a user with a convenient user interface.}}

\newglossaryentry{gps_tracker}{name={GPS\_Tracker},description={A name of the framework and as well a name for the backend software running for processing and storing telemetry data}}

\newglossaryentry{gps_android}{name={GPS\_Android},description={An Android application to send the telemetry information about the current mobile network from the users' phones to GPS_Tracker.}}

\newglossaryentry{telemetry}{name={Telemetry},description={Messages from the phones insalled \gls{gps_android}. Includes RSS level, uplink/downlink throughput measurement, GPS coordinates.}}

\newglossaryentry{broker}{name={Broker},description={A special architectural pattern, program, that is the point of communication between components.}}

\newglossaryentry{mqtt}{name={MQTT},description={Message Queuing Telemetry Transport, an publisher/subscriber-based application protocol running over TCP/IP, suitable for IoT application.}}

\newglossaryentry{json}{name={JSON},description={JavaScript Object Notation, a lightweight data-interchange format.}}

\newglossaryentry{mongodb}{name={MongoDB},description={ A NoSQL database storing data in BSON (Binary JSON) format.}}

\newglossaryentry{celery}{name={Celery},description={A framework to implement a program using "Worker" architecture design.}}

\newglossaryentry{rabbitmq}{name={RabbitMQ},description={An in-memory queuing message broker.}}

\newglossaryentry{user_equipment}{name={User Equipment},description={A mobile terminal which transmits data via the radio link.}}

\newglossaryentry{access_point}{name={AP},description={A Wi-Fi access point running by a laptop with an external	Wi-Fi adapter. Each laptop has a side application to support throughput	measurement.}}

\newglossaryentry{command_n_center}{name={Command Center},description={A central server where the system core is running. All measurement analysis and UI interactions perform here.}}

\newglossaryentry{unmanned_aerial_vehicle}{name={Unmanned Aerial Vehicle},description={A vehicle having AP on the board.}}


\newglossaryentry{received_signal_strength}{name={Received Signal Strength},description={Received Signal Strength - the estimated value of signal power for the radio signal. The greater the RSS value, the stronger the signal.}}


\newglossaryentry{gnss}{name={GNSS},description={Global Navigation Satellite System}}

\newglossaryentry{rss}{name={RSS},description={Received Signal Strength}}

\newglossaryentry{gps}{name={GPS},description={Global Positioning System}}

\newglossaryentry{ue}{name={UE},description={User Equipment}}

\newglossaryentry{uav}{name={UAV},description={Unmanned Aerial Vehicle}}




